### 2017-09-30 TF-vldb2018/sec-expt.tex

 We used the following settings.

@@

\ni (1) {\em \citationd}~\cite{citationWeb} contains 1.39M paper nodes and 3.02M paper-paper citation edges.
We used its undirected version, where edges indicate the relevance relationship. We generated 200 labels based on phrase clustering of paper titles.

@@

\ni (2) We adopted the LFR-benchmark graph model~\cite{AndreaSF08} to generate synthetic graphs (\synthetic) with community structure as existed in real-life networks. It is controlled by three parameters: the number $n$ of nodes, the average degree $d$ of nodes, and the number $l$ of node labels.
%Given $n, d$, and $l$, the generator produces a graph with $n$ nodes, $n*d/2$ edges, and the nodes are labeled from a set of $l$ labels.

@@

\etitle{Pattern generator}.
We implemented a generator to produce pattern graphs, controlled by 4 parameters:
the number of nodes $|V_P|$, the number of edges $|E_P|$, label $l_{P}$ for each node from
an alphabet of labels in the corresponding data graphs,
and capacity bound $f_{P}$ for each node.

\etitle{Algorithms}. We implemented the following algorithms, all in C++:
(1) algorithm \optgrouprec for \teamF; (2) incremental algorithm \inc for \dynteamF;
(3) three compared top-$k$ team formation algorithms \mindia, \minsumdis and \denalk, where
(a) \mindia is to minimize the team diameter~\cite{Lappas09}; 
%firstly proposed the team formation problem;
(b) \minsumdis is to minimize the sum of all-pair shortest distances of teams~\cite{Kargar11}; and
(c) \denalk is to maximize the team density~\cite{GajewarS12}. 
%which has the same goal with our algorithms; and
Among algorithms for \teamF, \minsumdis is able to find top-$k$ teams in polynomial time, which is an adaption of Lawler's procedure.
Based on this, we extend \mindia and \denalk to find top-$k$ teams in polynomial time.

@@

We present our findings. In all the experiments, we set $k=10$, $r=2$, $h=3$, $(|V_{P}|,$ $|E_{P}|)$ to be (10,12),
and capacity bounds to be [1,10] by default.
When generating synthetic graphs, we fixed $n=10^7$, $d=10$ and $l=200$.
All the findings on \youtube are reported in the Appendix.

>>>>

 We used the following datasets and settings.

@@

\ni (1) {\em \citationd}~\cite{citationWeb} is a real-life dataset containing 1.39M paper nodes and 3.02M paper-paper citation edges.
We used its undirected version, where edges indicate the relevance relationship. We generated 200 node labels based on phrase clustering of paper titles.

@@

\ni (2) We generated synthetic data graphs (\synthetic) with community structures as existed in real-life networks, by adopting the LFR-benchmark graph model~\cite{AndreaSF08}. It is controlled by three parameters: the number $n$ of nodes, the average degree $d$ of nodes, and the number $l$ of node labels.
%Given $n, d$, and $l$, the generator produces a graph with $n$ nodes, $n*d/2$ edges, and the nodes are labeled from a set of $l$ labels.

@@

\etitle{Pattern generator}.
We implemented a generator to produce pattern graphs, controlled by 4 parameters:
the number of nodes $|V_P|$, the number of edges $|E_P|$, the label $l_{P}$ for each node from
an alphabet of labels in the corresponding data graphs,
and the capacity bound $f_{P}$ for each node.

\etitle{Algorithms}. We implemented the following algorithms, all in C++:
(1) algorithm \optgrouprec for \teamF; (2) incremental algorithm \inc for \dynteamF;
(3) three compared top-$k$ team formation algorithms \mindia, \minsumdis and \denalk, where
(a) \mindia is to minimize the team diameter~\cite{Lappas09}, and is firstly proposed for the team formation problem;
(b) \minsumdis is to minimize the sum of all-pair shortest distances of teams~\cite{Kargar11}; and
(c) \denalk is to maximize the team density~\cite{GajewarS12}, which has the same goal with our algorithms.
Among algorithms for \teamF, most of them including  \mindia and \denalk only compute the best team,
while \minsumdis is able to find top-$k$ teams in polynomial time, which is an adaption of Lawler's procedure.
Based on this, we extend \mindia and \denalk to find top-$k$ teams in polynomial time.

@@

We present our findings. In all the experiments, we set $k=10$, $r=2$, $h=3$, $(|V_{P}|,$ $|E_{P}|)$ to be (10,12),
and capacity bounds to be [1,10] by default.
When generating synthetic graphs, we fixed $n=10^7$, $d=10$ and $l=200$.
Aqll the findings on \youtube are reported in the Appendix.
